The \frb\ Observing Campaign: Multi-Telescope Radio Burst and Implications for the FRB Population

### 2016-12-21 repeater-vladata.tex
through maura comments. need to redo dm change analysis

\begin{abstract}
The millisecond radio transients known as Fast Radio Bursts have recently emerged as a mysterious, new class of astrophysical transient. The recent localization of \frb\ has helped identify its host galaxy, measure its distance, and infer intrinsic properties that comment on the broader FRB population. We present a detailed analysis of these bursts, including the first simultaneous detection of an FRB with multiple telescopes. We show that the burst spectra typically have a broad Gaussian shape on the scale of $\sim500$~MHz with fine spectral structure consistent with either scintillation or unresolved intrinsic temporal structure. We present the luminosity distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb. We close with thoughts on optimal strategies to make new interferometric localizations of FRBs.
\end{abstract}

@@

\frb\ has now been localized four orders of magnitude better than any other FRB and placed at a cosmological distance. Its lookback and luminosity distances are 746 and 972 Mpc \citep{2016A&A...594A..13P}, which are orders of magnitude larger than any other millisecond transient. This shows that FRBs are more luminous than any other millisecond radio transient, have a significant DM contribution from the IGM, and can be used to probe the IGM and their host galaxy. The promise implied by the first reported FRB \citep{2007Sci...318..777L} is now being realized.

@@

We can also assume that \frb\ is representative and use it to constrain the physical processes at play in the overall FRB population. In this case, we know that FRBs are luminous, but it is not yet clear what process generates the radio bursts themselves \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}. The simultaneous \frb\ observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI-LA gives a more complete picture of the spectral structure of FRB radio emission. FRB repetition also has strong implications for the number of FRB-generating systems in the universe \citep{2016MNRAS.458L..89C}.

@@

\begin{figure*}[ht]
\begin{center}
 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.4\columnwidth]{spec_57623.png}
  \includegraphics[width=0.4\columnwidth]{spec_57633_scan7.png}
  \includegraphics[width=0.4\columnwidth]{spec_57633_scan13.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.4\columnwidth]{spec_57638.png}
  \includegraphics[width=0.4\columnwidth]{spec_57643.png}
  \includegraphics[width=0.4\columnwidth]{spec_57645.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.4\columnwidth]{spec_57646.png}
  \includegraphics[width=0.4\columnwidth]{spec_57648.png}
  \includegraphics[width=0.4\columnwidth]{spec_57649.png}
 \end{minipage}
\caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz. Starting at the top left (moving right and then down), they correspond to bursts on MJDs 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649. Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
The solid line is a best-fit Gaussian model derived from spectra binned by a factor of 4.
\label{fig:spec}}
\end{center}
\end{figure*}

@@

\subsubsection{Dispersion}
The initial VLA detections were made by searching a DM grid that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta DM=10 \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}. In optimizing detection significance over a fine DM grid, we find optimal DM values range from 552 to 572 pc cm$^{-3}$. However, the uncertainty in the peak DM measurement is defined by the DM sensitivity loss curve and the significance of the burst.

Given that the apparent DM can potentially change due to intrinsic or extrinsic effects, we developed a more sophisticated system for modeling dispersion. We created a generative model to sample the likelihood distribution of a class of dispersion models \citep{2010arXiv1008.4686H}. We use the Gaussian shape (see \S \ref{sec:spec}) along the spectral axis and apply a frequency-depndent delay for a given dispersion model. The likelihood is directly sampled by calculating the product of probabilities on a per-pixel basis of the 2-dimensional dynamic spectrum. Uncertainties in each pixel are drawn from a uniform Gaussian error distribution that is estimated from the data.

@@

\subsubsection{Spectral Autocorrelation}
\label{sec:auto}
Autocorrelation of the burst signal (both temporal and spectral) can be used to infer both intrinsic properties and modulation due to scintillation \citep{CORDES}. While VLA spectral resolution of 4~MHz is relatively coarse, the Galactic electron density model predicts a diffractive scintillation bandwidth of {\color{red}Jim: xx MHz at 3~GHz} \citep{2002astro.ph..7156C}. Figure \ref{fig:acf} shows the spectral autocorrellation for the strongest burst (MJD 57633.68). No excess correlation is found near the channel resolution, which limits the correlation width to less than 4~MHz.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{acf_57633_scan7}
\caption{ {\color{red} Jim: worth keeping?} The spectral autocorrelation for the burst from \frb\ at MJD 57633.68. Blue shows the autocorrelation for the burst and green shows an autocorrelation of a representative spectrum with no burst.
\label{fig:acf}}
\end{center}
\end{figure}

@@

\subsection{Luminosity and Brightness Distribution}
\label{sec:disn}
Knowing the burst distance, we calculate their mean luminosity across a single 5~ms integration and the 1~GHz bandwidth (Table \ref{tab:spec}). The VLA has also shown for the first time that most bursts are contained within the 3~GHz band. That means that the mean S-band flux density can be converted to a luminosity in units of ergs with no assumptions about its spectral properties.

This uniform sample of burst luminosities can be used to infer more general properties of \frb. We treat the detection probability as a Poisson process with a rate that scales with the luminosity as a powerlaw. Figure \ref{fig:lumd} shows the probability distribution for the powerlaw amplitude and index for the sample of nine VLA bursts. The luminosity powerlaw index $1\sigma$\ bounds range from --0.5 to +0.4; for a cumulative luminosity distribution, this corresponds to a powerlaw index of roughly --0.6. The flatness of the distribution is also clear from range of significance of the nine bursts (12 to 179$\sigma$). All bursts are much brighter than the sensitivity limit, so the distribution is not affected by a completeness limit.

@@

\includegraphics[width=0.9\columnwidth]{luminosity_disn}
\caption{\emph{Top:} Cumulative luminosity distribution with powerlaw fit for the nine VLA bursts from \frb. \emph{Bottom:} Probability distribution of luminosity model of the differential luminisotiy distribution. The powerlaw is referenced to $L=2\times10^{38}$\ erg.
\label{fig:lumd}}
\end{center}
\end{figure}

Assuming that \frb\ is representative of the overall FRB population, we can use the luminosity distribution of the former to infer properties of the latter. The primary observable of the FRB population is the flux distribution. We use a Monte-Carlo technique to simulate an FRB population with a given luminosity and spatial distribution. To reproduce the observed FRB sample, we select the brightest $N$\ bursts and fit their fluxes with a powerlaw. The tail of this distribution selects for extrema, such cut-offs in the intrinsic distribution or propagation effects \citep{2015MNRAS.451.3278M, CORDES}. Therefore, we sample 100 such populations and measure 95\% bounds on the distribution of cumulative flux distribution index.

@@

\subsection{Emission Physics and Burst Energetics}
The measurement of a redshift to the host of \frb\ allows us to measure the burst luminosity. We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo. This confirms the results presented in \citet{LOC}, which quoted a luminosity on the order of $10^{38}$\ erg. The more refined analysis presented here measures somewhat higher burst fluxes, so the brightest VLA burst luminosity is now on the order of $10^{40}$\ erg.

However, the total energy emitted by \frb\ can be orders of magnitude different than this isotropic, apparent luminosity. While the emission process is not yet known, it is neccessarily coherent \citep{2016Natur.531..202S, WEIRD}, so relativistical beaming will amplify the apparent brightness. Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways \citep{CORDES} and the duration of the emission in the source frame is not known. In any case, the luminosity scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.

@@

**Discussion of luminosity/flux distribution analysis presented in \S \ref{sec:disn})**

@@

\subsection{Repetition}
The burst rate analysis presented in \S \ref{sec:temp} shows that the detection probability of \frb\ is not stationary. As mentioned above, this could be caused by intrinsic events (e.g., magnetar outburst) or propagation effects. In either case, it demonstrates that \frb\ has a kind of "red spectrum" temporally, in which bursts tend to cluster in time \citep{2016MNRAS.458L..89C}. The detection of a burst improves odds of finding more bursts in near-future observations.

If this statistical property describes other FRBs, it weakens previous constraints on repetition \citep{2015MNRAS.454..457P,2015ApJ...807...16L}. It is possible that other FRBs have repeating bursts, although calculating a limit requires knowing the temporal powerlaw that defines the repetition. Observations of \frb\ have not yet detected enough bursts to reliably measure that index. This repetition also implies that there are fewer phyiscal sources of FRBs than implied by the burst detection rate.

\subsection{FRB Rate}
% cut from gemini paper. TODO: incorporate referee comments on rate scale. Sarah?
{\color{red} Sarah: can you update this as a per-SFR rate?}
Assuming that \frb\ is from the same population as the other FRBs, the measurement of a distance for the host of \frb\ allows us to re-evaluate the cosmic volume and event rate per galaxy for the FRB population. The estimated projected FRB rate $R_p$\ understates the true rate by a beaming fraction $\Omega_b$\ \citep[$\sim$10\%;][]{1998MNRAS.298..625T}.. For a comoving volume $V(z)$\ and galaxy number density $\Phi(M)$, the rate per galaxy is $R_{FRB} = R_p /(\Omega_b \Phi(M)V (z))$.

The first such rate estimate was made by \citet{2013Sci...341...53T}, who used the measured DM to estimate a characteristic distance for their sample of 4 FRBs. They assumed that all of the extragalactic component of the DM was caused by the IGM and scaled as $DM\approx z\times1200 \rm{pc}\ \rm{cm}^{-3}$\ \citep{2003ApJ...598L..79I,2004MNRAS.348..999I}. They also calculated the number of galaxies by assuming a characteristic $L_*$\ galaxy \citep[corresponding to stellar mass $M_* \approx 1010.66 M$;][]{2012MNRAS.421..621B}.

Our calculation differs in that we have better estimates of all three parameters. First, the projected FRB rate is now believed to be closer to $2\times10^3 \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms \citep{2016arXiv161100458L,2016MNRAS.460L..30C}. \frb\ is associated with a relatively small galaxy, which are roughly a factor of 100 more abundant \citep[$\Phi(M) \approx 10^{-2} \rm{Mpc}^{-3}$;][]{2007ApJ...665..265F}. Finally, the measured distance for FRB 121102 suggests that roughly half of the extragalactic DM is intrinsic to the host and half is from the IGM.

This reduces the characteristic distance by a factor of two and the volume by an order of magnitude. Considering these factors, we assume a characteristic FRB redshift of 0.4 to estimate $R_{FRB} \approx 10^{-4} (0.1/\Omega_b) \rm{galaxy}^{-1} \rm{year}^{-1}$, which is two orders of magnitude lower than previously estimated \citep[assuming isotropic radiation;]{2013Sci...341...53T}.

@@

\subsection{Observing Strategies}
As discussed above, \citet{2016MNRAS.458L..89C} note that the FRB repetition implies that the number of FRB-generating sources is smaller than the number of bursts. In some scenarios, this means that there are areas on the sky that may contain no FRBs. Wide, shallow surveys are the preferred strategy for blind detection of FRBs. However, future efforts to localize FRBs are still most likely to success by targeting known FRBs to catch repetitions. Finally, we note that the spectral coverage of bursts from \frb\ are relatively narrow ($<1$~GHz) and change dramatically between bursts. Thus, the odds of detecting a burst will improve linearly with bandwidth for bandwidths wider than this characteristic scale.

\subsection{Naming Convention}
The consistency of \frb\ properties (e.g., luminosity distribution) with the overall population suggests other FRBs likely repeat. If so, the current naming convention for FRBs (analogous to cataclysmic supernovae), will likely become uninformative, especially as large FRB survey projects come online \citep{2014SPIE.9145E..22B}. If all FRBs repeat, then a more useful convention would be based on coordinates. However, there are already two FRBs that have consistent celestial positions and different DMs. Therefore, we suggest an FRB naming convention as Jhhmm+ddDMmmmm.

@@

We presented the first multi-telescope detection (Arecibo and VLA) of a FRB. By detecting this burst from 1.2 to 4.5~GHz, we have demonstrated that some bursts have broad spectral structure. However, three other VLA bursts are undetected by Arecibo. That, combined with the measurement of spectra within the VLA band, suggest that the typical burst has a characteristic Gaussian spectral shape with width $\sim500$\ MHz.

@@

Analysis of the VLA burst times shows that the burst rate is highly variable. This shows that past constraints on FRB repetition are weaker than previously inferred. The combination of relatively narrow spectral structure, flat luminosity and flux distributions, and variable burst rate suggests that repeated observations, wide bandwidth, and large instantaneous field of view all improve the chance of detection.

@@

\section*{Acknowledgements}
This project was supported by the University of California Office of the President under Lab Fees Research Program Award 237863. The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc.. This research made use of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).

>>>>

\begin{abstract}
The millisecond radio transients known as Fast Radio Bursts have recently emerged as a mysterious, new class of astrophysical transient. The recent localization of \frb\ has helped identify its host galaxy, measure its distance, and infer intrinsic properties that comment on the broader FRB population. We present a detailed analysis of these bursts, including the first simultaneous detection of an FRB with multiple telescopes. We show that the burst spectra typically have a broad Gaussian shape on the scale of $\sim500$~MHz with fine spectral structure consistent with either scintillation or unresolved intrinsic temporal structure. We present the burst energy distribution and temporal statistics for \frb\ and argue that the whole FRB population is adequately described by a single class similar to \frb. We close with thoughts on optimal strategies to make new interferometric localizations of FRBs.
\end{abstract}

@@

\frb\ has now been localized four orders of magnitude better than any other FRB and placed at a cosmological distance. Its lookback and luminosity distances are 746 and 972 Mpc \citep{2016A&A...594A..13P}, which are orders of magnitude larger than any other millisecond transient. This shows that FRBs are more energetic than any other millisecond radio transient, have a significant DM contribution from the IGM, and can be used to probe the IGM and their host galaxy. The promise implied by the first reported FRB \citep{2007Sci...318..777L} is now being realized.

@@

We can also assume that \frb\ is representative and use it to constrain the physical processes at play in the overall FRB population. In this case, we know that FRBs are apparently luminous, but it is not yet clear what processes are responsible. Possibilities include intrinsic processes, such as coherent, pulsar-like emission \citep{2014PhRvD..89j3009K, 2014ApJ...785L..26L, 2016MNRAS.457..232C}, or extrinsic effects like scintillation \citep{CORDES}. The simultaneous \frb\ observing campaign with the VLA, Arecibo, Effelsberg, GBT, and AMI-LA gives a more complete picture of the spectral structure of FRB radio emission. FRB repetition also has strong implications for calculations of their rate of occurrence \citep{2016MNRAS.458L..89C} and comparison to other classes of transient, such as superluminous supernovae \citep{OPT}.

@@

\begin{figure*}[ht]
\begin{center}
 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.33\columnwidth]{spec_57623.png}
  \includegraphics[width=0.33\columnwidth]{spec_57633_scan7.png}
  \includegraphics[width=0.33\columnwidth]{spec_57633_scan13.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.33\columnwidth]{spec_57638.png}
  \includegraphics[width=0.33\columnwidth]{spec_57643.png}
  \includegraphics[width=0.33\columnwidth]{spec_57645.png}
 \end{minipage}

 \begin{minipage}{2\columnwidth}
  \includegraphics[width=0.33\columnwidth]{spec_57646.png}
  \includegraphics[width=0.33\columnwidth]{spec_57648.png}
  \includegraphics[width=0.33\columnwidth]{spec_57649.png}
 \end{minipage}
\caption{Spectra of nine bursts seen by the VLA from 2.5 to 3.5~GHz. Starting at the top left (moving right and then down), they correspond to bursts on MJDs 57623, 57633.68, 57633.70, 57638, 57643, 57645, 57646, 57648, and 57649. Note that bursts are detected in 5~ms images generated from dedispersed visibilities.
The solid line is a best-fit Gaussian model derived from spectra binned by a factor of 4.
\label{fig:spec}}
\end{center}
\end{figure*}

@@

\subsubsection{Dispersion}
The initial VLA detections were made by searching a DM grid that allowed inter-DM sensitivity losses up to roughly 10\% \citep[$\Delta DM=10\ \rm{pc}\ \rm{cm}^{-3}$][]{2003ApJ...596.1142C}. In optimizing detection significance over a fine DM grid, we find optimal DM values range from 552 to 572 pc cm$^{-3}$. However, the uncertainty in the peak DM measurement is defined by the signal-to-noise of the burst and how this changes with DM.

Given that the apparent DM can potentially change due to intrinsic or extrinsic effects, we developed a more sophisticated system for modeling dispersion. We created a generative model to sample the likelihood distribution as a function of DM \citep{2010arXiv1008.4686H}. We use the Gaussian shape (see \S \ref{sec:spec}) along the spectral axis and apply a frequency-dependent delay for a given dispersion model. The likelihood is directly sampled by calculating the product of probabilities on a per-pixel basis of the 2-dimensional dynamic spectrum. Uncertainties in each pixel are drawn from a uniform Gaussian error distribution that is estimated from the data.

@@

\subsubsection{Spectral Autocorrelation}
\label{sec:auto}
Autocorrelation of the burst signal (both temporal and spectral) can be used to infer both intrinsic properties and modulation due to scintillation \citep{CORDES}. Figure \ref{fig:acf} shows the spectral autocorrellation for the strongest burst (MJD 57633.68). The is no strong excess correlation near the channel resolution, which limits the correlation width to less than roughly 4~MHz. This is broadly consistent with expectations of Galactic diffractive scintillation bandwidth \citep[3--9~MHz near 3~GHz][]{2002astro.ph..7156C}.

\begin{figure}[htb]
\begin{center}
\includegraphics[width=0.9\columnwidth]{acf_57633_scan7}
\caption{The spectral autocorrelation as a function of frequency for the burst from \frb\ at MJD 57633.68. Black dots show the autocorrelation for the burst and cyan shows the autocorrelation of a representative spectrum with no burst.
\label{fig:acf}}
\end{center}
\end{figure}

@@

\subsection{Energy and Brightness Distribution}
\label{sec:disn}
Knowing the burst distance, we calculate their total energy by integrating flux in time and frequency (Table \ref{tab:spec}). The VLA has also shown for the first time that many bursts are contained within the 3~GHz band. For those bursts, the mean S-band flux density can be converted to an energy with no assumptions about its spectral properties.

This uniform sample of burst energies can be used to infer more general properties of \frb. We treat the detection probability as a Poisson process with a rate that scales with the energy as a powerlaw. Figure \ref{fig:lumd} shows the probability distribution for the powerlaw amplitude and index for the sample of nine VLA bursts. The energy powerlaw index $1\sigma$\ bounds range from --0.5 to +0.4; for a cumulative energy distribution, this corresponds to a powerlaw index of roughly --0.6. The flatness of the distribution is also clear from range of significance of the nine bursts (12 to 179$\sigma$). All bursts are much brighter than the sensitivity limit, so the distribution is not affected by a completeness limit. **elaborate on limit and completeness**

@@

\includegraphics[width=0.9\columnwidth]{luminosity_disn}
\caption{\emph{Top:} Cumulative energy distribution with powerlaw fit for the nine VLA bursts from \frb. \emph{Bottom:} Probability distribution of energy model of the differential luminisotiy distribution. The powerlaw is referenced to $L=2\times10^{38}$\ erg.
\label{fig:lumd}}
\end{center}
\end{figure}

Assuming that \frb\ is representative of the overall FRB population, we can use the energy distribution of the former to infer properties of the latter. The primary observable of the FRB population is the flux distribution. We use a Monte-Carlo technique to simulate an FRB population with a given energy/luminosity and spatial distribution. To reproduce the observed FRB sample, we select the brightest $N$\ bursts and fit their fluxes with a powerlaw. The tail of this distribution selects for extrema, such cut-offs in the intrinsic distribution or propagation effects \citep{2015MNRAS.451.3278M, CORDES}. Therefore, we sample 100 such populations and measure 95\% bounds on the distribution of cumulative flux distribution index.

@@

\subsection{Emission Physics and Burst Energetics}
The measurement of a redshift to the host of \frb\ allows us to measure the burst luminosity and energy. We now know that \frb\ is detectable with the VLA out to $z=0.7$\ and much farther with Arecibo. This confirms the results presented in \citet{LOC}, which quoted a energy on the order of $10^{38}$\ erg. The more refined analysis presented here results in somewhat higher burst fluxes, so the brightest VLA burst energy ranges as high as $5\times10^{39}$\ erg.

However, the total energy emitted by \frb\ can be orders of magnitude different than this isotropic, apparent energy. While the emission process is not yet known, it is neccessarily coherent \citep{2016Natur.531..202S, WEIRD}, so relativistical beaming will amplify the apparent brightness. Propagation effects (e.g., scintillation, scattering) can also modify the radio signal in a variety of ways \citep{CORDES} and the duration of the emission in the source frame is not known. In any case, the energy scale is still larger than any Galactic class of fast radio transient and requires either a new process or dramatic scaling of known emission processes \citep{2016MNRAS.462..941L, 2016MNRAS.457..232C}.

@@

**Discussion of energy/flux distribution analysis presented in \S \ref{sec:disn})**

@@

\subsection{Repetition}
The burst rate analysis presented in \S \ref{sec:temp} shows that the detection probability of \frb\ is not stationary. As mentioned above, this could be caused by intrinsic events (e.g., magnetar outburst) or propagation effects. While a detailed analysis of temporal correlation will require more bursts and/or more sophistication, it is clear that \frb\ has significant correlation on short timescales \citep[sometimes called a ''red spectrum'';][]{2016MNRAS.458L..89C}. Another way of stating this is that the detection of a burst improves odds of finding more bursts in near-future observations.

If this statistical property describes other FRBs, it weakens previous constraints on repetition \citep{2015MNRAS.454..457P,2015ApJ...807...16L}. It is possible that other FRBs have repeating bursts, although calculating a limit requires knowing the temporal correlation function that defines the repetition.  Repetition also implies that there are fewer phyiscal sources of FRBs than implied by the burst detection rate.

\subsection{FRB Rate}
% cut from gemini paper. TODO: incorporate referee comments on rate scale. Sarah?
{\color{red} Sarah: can you update this as a per-SFR rate?}
Assuming that \frb\ is from the same population as the other FRBs, the measurement of a distance for the host of \frb\ allows us to re-evaluate the cosmic volume and event rate per galaxy for the FRB population. The estimated projected FRB rate $R_p$\ understates the true rate by a beaming fraction $\Omega_b$\ \citep[$\sim$10\%;][]{1998MNRAS.298..625T}. For a comoving volume $V(z)$\ and galaxy number density $\Phi(M)$, the rate per galaxy is $R_{FRB} = R_p /(\Omega_b \Phi(M)V (z))$.

The first such rate estimate was made by \citet{2013Sci...341...53T}, who used the measured DM to estimate a characteristic distance for their sample of 4 FRBs. They assumed that all of the extragalactic component of the DM was caused by the IGM and scaled as $DM\approx z\times1200 \rm{pc}\ \rm{cm}^{-3}$\ \citep{2003ApJ...598L..79I,2004MNRAS.348..999I}. They also calculated the number of galaxies by assuming a characteristic $L_*$\ galaxy \citep[corresponding to stellar mass $M_* \approx 1011 M$;][]{2012MNRAS.421..621B}.

Our calculation differs in that we have better estimates of all three parameters. First, the projected FRB rate is now believed to be closer to $2\times10^3\ \rm{sky}^{-1} \rm{day}^{-1}$\ at high Galactic latitudes and flux densities brighter than 1 Jy ms \citep{2016arXiv161100458L,2016MNRAS.460L..30C, 2016MNRAS.455.2207R}. \frb\ is associated with a relatively small galaxy ($5\times10^7$\ Msun), which are roughly a factor of 100 more abundant \citep[$\Phi(M) \approx 10^{-2} \rm{Mpc}^{-3}$;][]{2007ApJ...665..265F}. Finally, the measured distance for FRB 121102 suggests that the extragalactic DM has comparable contributions from the IGM and host galaxy.

This reduces the characteristic distance by a factor of two and the volume by an order of magnitude. Considering these factors, we assume a characteristic redshift of the population that is twice that of \frb\ to estimate $R_{FRB} \approx 10^{-4} (0.1/\Omega_b) \rm{galaxy}^{-1} \rm{year}^{-1}$, which is two orders of magnitude lower than previously estimated \citep[assuming isotropic radiation;]{2013Sci...341...53T}.

@@

\subsection{Observing Strategies}
As discussed above, \citet{2016MNRAS.458L..89C} note that the FRB repetition implies that the number of FRB-generating sources is smaller than implied by the number of bursts. In some scenarios, this means that there are areas on the sky that may contain no FRBs. Wide, shallow surveys are the preferred strategy for blind detection of FRBs. However, future efforts to localize FRBs are still most likely to succeed by targeting known FRBs to catch repetitions, assuming that all FRBs repeat. Finally, we note that the average spectral coverage of bursts from \frb\ are relatively narrow ($<1$~GHz) and the coverage changes dramatically between bursts. Thus, the odds of detecting a burst will improve linearly with bandwidth for bandwidths wider than this characteristic scale.

%\subsection{Naming Convention}
%The consistency of \frb\ properties (e.g., energy distribution) with the overall population suggests other FRBs likely repeat. If so, the current naming convention for FRBs (analogous to cataclysmic supernovae), will likely become uninformative, especially as large FRB survey projects come online \citep{2014SPIE.9145E..22B}. If all FRBs repeat, then a more useful convention would be based on coordinates. However, there are already two FRBs that have consistent celestial positions and different DMs. Therefore, we suggest an FRB naming convention as Jhhmm+ddDMmmmm.

@@

We presented the first multi-telescope detection (Arecibo and VLA) of an FRB. By detecting this burst from 1.2 to 4.5~GHz, we have demonstrated that some bursts have broad spectral structure. However, three other VLA bursts are undetected by Arecibo. That, combined with the measurement of spectra within the VLA band, suggest that the typical burst has a characteristic Gaussian spectral shape with width $\sim500$\ MHz.

@@

Analysis of the VLA burst times shows that the burst rate is highly variable. This shows that past constraints on FRB repetition are weaker than previously inferred. The combination of relatively narrow spectral structure, flat energy and flux distributions, and variable burst rate suggests that repeated observations, wide bandwidth, and large instantaneous field of view all improve the chance of detection.

@@

\section*{Acknowledgements}
The National Radio Astronomy Observatory is a facility of the National Science Foundation operated under cooperative agreement by Associated Universities, Inc..
This project was supported by the University of California Office of the President under Lab Fees Research Program Award 237863. MAM is supported by NSF award \#1458952.
This research made use of Astropy, a community-developed core Python package for Astronomy (Astropy Collaboration, 2013).
